Halo alignments with large scale tidal and velocity fields

### 2013-05-16 paper/main.tex
complete table for the spin alignment

TABLA
\begin{table*}
\begin{tabular}{cccccc}\hline\hline
Author & Web Method & Spatial Scale & Test Direction &
Alignment & Mass dependence\\\hline

\cite{AragonCalvo2007} & Hessian density field & - &
perpendicular to sheet & $-$$-$ & $>10^{12}$\hMsun\\

& & - &
perpendicular to sheet & $-$ & $<10^{12}$\hMsun\\

& & - &
along the filament& $-$ & $>10^{12}$\hMsun\\

& & - &
along the filament& $+$ & $<10^{12}$\hMsun\\

\cite{Hahn2007} & Tidal Web & $2.1$\hMpc & along
the filament & $-$& none\\

& &  $2.1$\hMpc &
perpendicular to sheet & $-$$-$ & stronger $>10^{12}$\hMsun\\

\cite{Hatton2001} & Neighbors$^1$ &  & & 0\\\hline\hline

\end{tabular}\\
\caption{Summary of previous theoretical results.
NOTES:
$^1$ They do not use a web finder method. They look for correlations
with neightborig structures on any escale.
Angular Momentum}
\end{table*}

@@

The simulation has $2048^3$ particles in a bos of $250$\hMpc,
corresponding to a particles mass of $1.3\times 10^{8}$\hMsun.  Halos
are found using a FOF halo finder with $b=0.17$. The catalog only
include halos more massiven than $3\times 10^{9}$\hMsun.

@@

The aligmnet signal of the spin is very weak while the shape alignment
signal is very strong. The alignment is such that the eigenvector
corresponding to the smalles eigenvalue is aligned with the major
axis. This effect is stronger for more massive halos. 
In other words the major axis of a halo is aligned with a filament,
and lies on the plane that define a sheet.

@@

The environment is found using the hessian of the density. The density
field was interpolated over a $1024^3$ grid and then smoothed with a
Gaussian filter of scale $R_{s}2.1$\hMpc. There are two methods to
define the direction of a filament. The first method uses the
eigenvalues of the hessian density, howevere they define the filament
direction with the eigenvector corresponding the single positive
eigenvalue of the hessian. The second method used a line that
connects the two terminal halos in a filament segment.

>>>>

TABLA
\begin{table*}
SPIN
\begin{tabular}{cccccc}\hline\hline
Author & Web Method & Spatial Scale & Along &
Alignment & Mass dependence\\\hline

\cite{Libeskind2013} & V-Web & $1 \hMpc$ & 
filament &$-$ & $>10^{12}$\hMsun\\

&   & & 
filament &$+$ & $<10^{12}$\hMsun\\

&   & & 
wall & $++$ & all masses\\

\cite{Trowland2013} & Hessian density & $2-5\hMpc$ & 
filament & $-$ & $> 5\times 10^{12}$\hMsun\\
&   & & 
filament & $+$ & $< 5\times 10^{12}$\hMsun\\

\cite{Codis2012} & Morse Theory \& Tidal Web & $1-5\hMpc$ & 
filament & $--$ & $>10^{12}$\hMsun \\

&   & & 
filament & $++$ & $<10^{12}$\hMsun \\

& & & 
wall & $++$ & all masses\\

\cite{Zhang2009}  & Hessian density field &  $2.1$\hMpc & 
filament & $++$ & only if anticorrelated with shape\\

& &  & 
filament & $--$ & only if correlated with shape\\

\cite{AragonCalvo2007} & Hessian density field & - &
wall & $++$ & $>10^{12}$\hMsun\\

& & - &
wall & $+$ & $<10^{12}$\hMsun\\

& & - &
filament& $-$ & $>10^{12}$\hMsun\\

& & - &
filament& $+$ & $<10^{12}$\hMsun\\

\cite{Hahn2007} & Tidal Web & $2.1$\hMpc & filament & $-$& none\\

& &  $2.1$\hMpc &
wall & $++$ & stronger $>10^{12}$\hMsun\\\hline \hline

\end{tabular}\\
\caption{Summary of previous theoretical results.
Angular Momentum}
\end{table*}

@@

The simulation has $2048^3$ particles in a box of $250$\hMpc,
corresponding to a particles mass of $1.3\times 10^{8}$\hMsun.  Halos
are found using a FOF halo finder with $b=0.17$. The catalog only
include halos more massiven than $3\times 10^{9}$\hMsun.

@@

The aligmnet signal of the spin is very weak while the shape alignment
signal is very strong. The shape alignment is such that the eigenvector
corresponding to the smallest eigenvalue is aligned with the major
axis. This effect is stronger for more massive halos. 
In other words the major axis of a halo is aligned with a filament,
and lies on the plane that define a sheet. However the spin is
antialgined with the filament for massive halos and weakly aligned for
low mass halos.

@@

The environment is found using the hessian of the density. The density
field was interpolated over a $1024^3$ grid and then smoothed with a
Gaussian filter of scale $R_{s} = 2.1$\hMpc. There are two methods to
define the direction of a filament. The first method uses the
eigenvalues of the hessian density, howevere they define the filament
direction with the eigenvector corresponding the single positive
eigenvalue of the hessian. The second method used a line that
connects the two terminal halos in a filament segment.
